### 2020-04-22 intro.tex
updated fig

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{section:introduction}

The Cray XK7 Titan supercomputer~\cite{olcf:titan} was the \#1 system in the world for a
very long time~\cite{top500list}, and has remained a critically important computer
system through the end of its life in the Summer of 2019. It defied
scale with 18,688 individual compute nodes and delivered tens of
billions of computing hours to the U.S. Department of Energy
mission-critical programs for nearly 7 years.

@@

Figure~\ref{fig:chronology} illustrates the chronology of the rework
cycles and stable periods as indicated by the number of GPU changes at
periodic inventories.
\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figs/chronology001.pdf}
  \caption{Volume of GPU swaps detected at inventories. The break-in
    period before 2014 involved working out mechanical assembly issues
    at PCIe connectors
    frequent dates.}
  \label{fig:chronology}
\end{figure*}
The first two rework cycles before 2014 can be characterized as a
break-in period on a new system that is first of its kind and pushes
many technological boundaries, in this case mainly regarding blade
mechanical assembly. The resulting field engineering generated high
GPU swap counts. Late 2013 begins a very long period of stable
operation with very few issues until about mid 2016, when GPU failures
begin to rise. This results in the final rework cycle, replacing
11,000 GPUs throughout much of 2017.

>>>>

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{section:introduction}
The Cray XK7 Titan supercomputer~\cite{olcf:titan} was the \#1 system in the world for a
very long time~\cite{top500list}, and has remained a critically important computer
system through the end of its life in the Summer of 2019. It defied
scale with 18,688 individual compute nodes and delivered tens of
billions of computing hours to the U.S. Department of Energy
mission-critical programs for nearly 7 years.

@@

\begin{figure*}[tb]
  \centering
  \includegraphics[width=\textwidth]{figs/chronology001.pdf}
  \caption{Volume of GPU swaps detected on Titan at inventories. Our
    analysis begins with units in place by 2014. A break-in period
    before 2014 involved working out mechanical assembly issues at
    PCIe connectors.}
  \label{fig:chronology}
\end{figure*}
Figure~\ref{fig:chronology} illustrates the chronology of the rework
cycles and stable periods as indicated by the number of GPU changes at
periodic inventories.
The first two rework cycles before 2014 can be characterized as a
break-in period on a new system that is first of its kind and pushes
many technological boundaries, in this case mainly regarding blade
mechanical assembly. The resulting field engineering generated high
GPU swap counts. Late 2013 begins a very long period of stable
operation with very few issues until about mid 2016, when GPU failures
begin to rise. This results in the final rework cycle, replacing
11,000 GPUs throughout much of 2017.
